---
title: "Compthinking1 assessment"
date: 2023-10-12
format: html
---

## Question 1

```{r}
#Assigned values to species codes GREG,MALL,etc.
species_codes <- c(GREG="Great Egret", MALL="Mallard",MAWR="Marsh Wren",KILL="Killdeer")

sightings = c("GREG", "GREG", "MALL", "MAWR", "KILL", "GREG")

#way to create a table where indexing sightings via species codes
table(species_codes[sightings])
```

## Question 2

Adding 1 to a POSIXct object adds a second as it is a date-time and the unit place of 1 corresponds to seconds. It is a vector object used to represent datetimes.

The default origin of POSIXct objects is UTC?

```{r}
#code to convert the number 0 to January 1, 2000 at noon in UTC using as.POSIXct()

as.POSIXct(0,"2000-01-01 12:00", tz="UTC")

```

I'm not sure what vector this becomes if you take the POSIXct class away.

## Question 3

x is a list, y is an element, and I'm not sure what z is.

## Question 4

In a data frame, elements of a list are columns since there is only one row (I think). In a dataframe, length() is equivalent to nrow() because each row is one element.
